---
title: "Simple Penguin Data Analysis"
author: "Maxine Paredes"
format: 
  html:
    output: docs
---

# Load Libraries and Data
```{r}
library(tidyverse)
library(palmerpenguins)
library(readr)
```

# Introduction
In this report, we analyze Palmer penguin data, downloaded directly from the web, perform basic cleaning, and create a scatter plot.

# Data Import
We read the data from the palmerpenguins package CSV on GitHub:

```{r}
data <- penguins
head(penguins)
```

# Data Cleaning
Remove rows with missing values:

```{r}
penguins_clean <- penguins %>%
  drop_na()
  ```
# Visualization
## Scatterplot of bill length vs flipper length, colored by species:

```{r}
ggplot(penguins_clean, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point(size = 2, alpha = 0.7) +
  theme_minimal() +
  labs(
    title = "Bill Length vs Flipper Length in Palmer Penguins",
    x = "Bill Length (mm)",
    y = "Flipper Length (mm)"
  )
  ```
# Conclusion

We loaded, cleaned, and visualized Palmer penguin data from the internet.
The plot shows species differences in bill and flipper length.